### 2019-03-22 Journal Version/2ECFDT.tex
journal

In Section \ref{binaryfdt} our focus was on binary MIPs. In this section, in an attempt to extend FDT to 0,1,2 problems we introduce an FDT algorithm for a 2-edge-connected multigraph problem. Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multigraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edge in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2. In the 2EC problem, we are given non-negative costs on the edge of $G$ and the goal is to find the minimum cost 2-edge-connected multigraph of $G$. Notice that, no optimal solution ever takes 3 copies of an edge in 2EC, hence we assume that we can take an edge at most 2 times. The natural linear programming relaxation is $\EC(G) = \{x\in [0,2]^E: x(\delta(U))\geq 2 \mbox{ for } \emptyset \subset U \subset V\}$. Notice that $\dom(\EC(G))\cap [0,2]^{E} = \EC(G)$, since 2EC is a covering problem. We want to prove Theorem \ref{FDT2EC}.
We do not know the exact value for $g_{\EC}$, but we know $\frac{6}{5} \leq g_{\EC} \leq \frac{3}{2}$ \cite{carr-ravi,Wolsey1980}. Also, we need to remark that polyhedral version of Christofides' algorithm provides a $\frac{3}{2}$-approximation for 2EC, i.e. we already have an algorithm with $C\leq \frac{3}{2}$. However, we showed in Section \ref{experiment} that in practice the constant $C$ for the FDT algorithm for 2EC is much better than $\frac{3}{2}$ for fundamental extreme points with 10 vertices.

@@

First, we need a branching lemma. Observe that  the following branching lemma is essentially a translation of Lemma \ref{LPClemma} for 0,1,2 problems except for one additional clause.

@@

\begin{proof}
	Consider the following LP with variables $\lambda_j$ and $x^j$ for $j=0,1,2$. 
	\begin{align}
		\quad\quad& \max\quad \;\sum_{j=0,1,2}\lambda_j\\
		&\;\text{s.t.} \quad x^j(\delta(U))\geq 2\lambda_j \;& \mbox{ for $\emptyset \subset U \subset V$, and $j=0,1,2$} \label{feasibility2ec}\\
		&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq 2\lambda_j\; &\mbox{ for $j=0,1,2$}\label{bound2ec}\\
		&\;{\color{white}{\text{s.t.}} }\quad x^j_e = j\; &\mbox{ for $j=0,1,2$}\label{branchcoordinate2ec}\\
		&\;{\color{white}{\text{s.t.}} }\quad x^j_f \geq j \; &\mbox{ for $f\in E$ where $x_f \geq 1$, and $j=0,1,2$}\label{1edges2ec}\\
		&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1+x^2 \leq x\label{packing2ec}\\
		&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1,\lambda_2 \geq 0
	\end{align}	Let $x^j$, $\gamma_j$ for $j=0,1,2$ be an optimal solution solution to the LP above. Let $\hat{x}^{j}=\frac{x^j}{\gamma_j}$ for $j=0,1,2$ where $\gamma_j>0$. If $\gamma_j=0$, let $\hat{x}^{j}=0$. Observe that  (ii), (iii), (iv), and (v) are satisfied with this choice. We can also show that $\gamma_0+\gamma_1+\gamma_2\geq \frac{1}{g_{\EC}}$, which means that (i) is also satisfied. The proof is similar to the proof of the claim in Lemma \ref{LPClemma}, but we need to replace each $f\in E$ with $x_f\geq 1$ with a suitably long path to ensure that Constraint (\ref{1edges2ec}) is also satisfied.	We skip the details.\iffalse{
	\begin{claim}\label{CVexists}
		We have $\gamma_0 + \gamma_1+\gamma_2\geq \frac{1}{g_{\EC}}$.
	\end{claim}
	\begin{proof}
		Suppose for contradiction $\sum_{j=0,1,2}\gamma_j = \frac{1}{g_{\EC}} - \epsilon$ for some $\epsilon >0$.

		Construct graph $G'$ by removing edge $f$ with $x_f\geq 1$ and replacing it with a path $P_f$ of length $\ceil{\frac{2}{\epsilon}}$. Define $x'_h = x_h$ for each edge $h$ such that $x_h<1$. For each $h\in P_f$ let $x'_h= x_f$ for all $f$ with $x_f\geq 1$. It is easy to check that $x'\in \EC(G')$. By Theorem \ref{CV} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and 2-edge-connected multigraphs $F'_i$ of $G'$ for $i=1,\ldots,k$ such that 
		$\sum_{i=1}^{k}\theta_i \chi^{F'_i}\leq g_{\EC}x'$.

		Note that each $F'_i$ contains at least one copy of every edge in any path $P_f$, except for at most one edge in the path. We will obtain 2-edge-connected multigraphs $F_1,\ldots,F_k$ of $G$ using $F'_1,\ldots,F'_k$, respectively. To obtain $F_i$ first remove all $P_f$ paths from $F'_i$. Suppose there is an edge $h$ in $P_f$ such that $\chi^{F'_i}_h=0$, this means that for any edge $p\in P_f$ such that $p\neq h$, $\chi^{F'_i}_p=2$. In this case, let $\chi^{F_i}_f=2$, i.e. add two copies of $f$ to $F_i$. If there is an edge $h\in P_f$ with $\chi^{F'_i}_h = 1$, let $\chi^{F_i}_f=1$, i.e. add one copy of $f$ to $F_i$. If for all edge $h\in P_f$, we have $\chi^{F'_i}_h=2$, then let $\chi^{F_i}_f=2$. For $f\in E$ with $x_f<1$ we have
		\begin{equation}
		\sum_{i=1}^{k}\theta_i \chi^{F_i}_f=\sum_{i=1}^{k}\theta_i \chi^{F'_i}_f\leq g_{\EC}x'_f= g_{\EC}x_f.
		\end{equation}
		In addition for $f\in E$ with $x_f\geq 1$ we have $\chi^{F_i}_f \leq \frac{\sum_{h\in P_f}\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}$ by construction.
		\begin{align*}
			\sum_{i=1}^{k}\theta_i \chi^{F_i}_f&\leq \sum_{i=1}^{k}\theta_i\frac{\sum_{h\in P_f}\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}\\
			&= \frac{\sum_{h\in P_f} \sum_{i=1}^{k}\theta_i\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}\\
			&\leq \frac{\sum_{h\in P_f} g_{\EC}x'_h}{\ceil{\frac{2}{\epsilon}}-1}\\
			&= \frac{\sum_{h\in P_f} g_{\EC}x'_h}{\ceil{\frac{2}{\epsilon}}-1}\\
			&= \frac{\ceil{\frac{2}{\epsilon}}}{\ceil{\frac{2}{\epsilon}}-1}g_{\EC}x_f
		\end{align*}
		Therefore, we have 
		\begin{equation}
		x' \geq \sum_{i\in [k]: \chi^{F_i}_e=1}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}+\sum_{i\in [k]: \chi^{F_i}_e=2}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}.
		\end{equation}
		Let $x^j = \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}$ and $\theta_j =  \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}$ for $j=0,1,2$. It is easy to check that $x^j$ , $\theta_j$ for $j=0,1,2$ is a feasible solution to the LP above. Notice that $\sum_{j=0,1,2}\theta_j = \frac{\ceil{\frac{2}{\epsilon}}-1}{g_{\EC}\ceil{\frac{2}{\epsilon}}}$. By assumption, we have $\frac{\ceil{\frac{2}{\epsilon}}-1}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\leq  \frac{1}{g_{\EC}}-\epsilon$. However, this means $2\leq 1$ which is a contradiction.
	\end{proof}
	This concludes the proof.}\fi \end{proof}

@@

\begin{lemma}\label{2ecpruning}
	The FDT algorithm for 2EC in  polynomial time produces sets $L_0,\ldots,L_t$ of pairs $x\in \EC(G)$ together with multipliers $\lambda$ with the following properties.
		(a) If $x\in L_i$, then $x_{e_j}=0$ or $x_{e_j}\geq 1$ for $j=1,\ldots,i$, (b) $\sum_{(x,\lambda)\in L_i }\lambda \geq \frac{1}{g_{\EC}^i}$, (c) $\sum_{(x,\lambda)\in L_i }\lambda x \leq x^*$, (d) $|L_i|\leq t$.
\end{lemma}
The proof is similar to Lemma \ref{prune}, but we need to use property (i) in Lemma \ref{LPC2EC} to prove that (a) also holds.
\iffalse{
\begin{proof}
	We proceed by induction on the $i$. Define $L_0=\{(x^*,1)\}$. It is easy to check all the properties are satisfied. Now, suppose by induction we have $L_{i-1}$ for some $i=1,\ldots,t$ that satisfies all the properties. For each solution $x^\ell$ in $L_{i-1}$ apply Lemma \ref{LPC2EC} on $x^\ell$ and $e_{i}$ to obtain $x^{\ell j}$ and $\lambda_{\ell j}$ for $j=0,1,2$. Let $L'$ be the collection that contains $(x^{\ell j},\lambda_\ell \cdot \lambda_{\ell j})$ for $j=0,1,2$, when applied to all $(x^\ell,\lambda_\ell)$ in $L_{i-1}$. Similar to the proof in Lemma \ref{prune} one can check that $L_i$ satisfies properties (b), (c). We now verify property (a). Consider a solution $x^\ell$ in $L_{i-1}$. For $e\in \{e_1,\ldots,e_{i-1}\}$ if $x^\ell_e =0$, then by property (iv) in Lemma \ref{LPC2EC} we have $x^{\ell j}=0$ for $j=0,1,2$. Otherwise by induction we have $x^{\ell}_{e}\geq 1$ in which case property (v) in Lemma \ref{LPC2EC} ensures that $x^{\ell j}_e\geq 1$ for $j=0,1,2$. Also, $x^{\ell j}_{e_i}= j$, so $x^{\ell j}_{e_i}=0$ or $x^{\ell j}_{e_i}\geq 1$ for $j=0,1,2$.

	If $|L'|\geq t$ we let $L_i=L'$, otherwise apply $\prun(L')$ to obtain $L_{i}$.
\end{proof}	}\fi

>>>>

In Section \ref{binaryfdt} our focus was on binary MILPs. In this section, in an attempt to extend FDT to \{0,1,2\} problems we introduce an FDT algorithm for a 2-edge-connected multigraph problem. Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multigraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edge in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2. In the 2EC problem, we are given non-negative costs on the edge of $G$ and the goal is to find the minimum cost 2-edge-connected multigraph of $G$. Notice that, no optimal solution ever takes 3 copies of an edge in 2EC, hence we assume that we can take an edge at most 2 times. The natural linear programming relaxation is $\EC(G) = \{x\in [0,2]^E: x(\delta(U))\geq 2 \mbox{ for } \emptyset \subset U \subset V\}$. Notice that $\dom(\EC(G))\cap [0,2]^{E} = \EC(G)$, since 2EC is a covering problem. We want to prove Theorem \ref{FDT2EC}.
\FDTEC*
We do not know the exact value for $g_{\EC}$, but we know $\frac{6}{5} \leq g_{\EC} \leq \frac{3}{2}$ \cite{carr-ravi,Wolsey1980}. Also, we need to remark that polyhedral version of Christofides' algorithm provides a $\frac{3}{2}$-approximation for 2EC, i.e. we already have an algorithm with $C\leq \frac{3}{2}$. However, we showed in Section \ref{experiment} that in practice the constant $C$ for the FDT algorithm for 2EC is much better than $\frac{3}{2}$ for FEPs of order 10.

@@

First, we need a branching lemma. Observe that  the following branching lemma is essentially a translation of Lemma \ref{LPClemma} for $\{0,1,2\}$ problems except for one additional clause.

@@

\begin{proof}
	Consider the following LP with variables $\lambda_j$ and $x^j$ for $j=0,1,2$. 
	\begin{align}
		\quad\quad& \max\quad \;\sum_{j=0,1,2}\lambda_j\\
		&\;\text{s.t.} \quad x^j(\delta(U))\geq 2\lambda_j \;& \mbox{ for $\emptyset \subset U \subset V$, and $j=0,1,2$} \label{feasibility2ec}\\
		&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq 2\lambda_j\; &\mbox{ for $j=0,1,2$}\label{bound2ec}\\
		&\;{\color{white}{\text{s.t.}} }\quad x^j_e = j\; &\mbox{ for $j=0,1,2$}\label{branchcoordinate2ec}\\
		&\;{\color{white}{\text{s.t.}} }\quad x^j_f \geq \lambda_j \; &\mbox{ for $f\in E$ where $x_f \geq 1$, and $j=0,1,2$}\label{1edges2ec}\\
		&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1+x^2 \leq x\label{packing2ec}\\
		&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1,\lambda_2 \geq 0
	\end{align}	Let $x^j$, $\gamma_j$ for $j=0,1,2$ be an optimal solution solution to the LP above. Let $\hat{x}^{j}=\frac{x^j}{\gamma_j}$ for $j=0,1,2$ where $\gamma_j>0$. If $\gamma_j=0$, let $\hat{x}^{j}=0$. Observe that  (ii), (iii), (iv), and (v) are satisfied with this choice. We can also show that $\gamma_0+\gamma_1+\gamma_2\geq \frac{1}{g_{\EC}}$, which means that (i) is also satisfied. The proof is similar to the proof of the claim in Lemma \ref{LPClemma}, but we need to replace each $f\in E$ with $x_f\geq 1$ with a suitably long path to ensure that Constraint (\ref{1edges2ec}) is also satisfied.	
	\begin{claim}\label{CVexists}
		We have $\gamma_0 + \gamma_1+\gamma_2\geq \frac{1}{g_{\EC}}$.
	\end{claim}
	\begin{proof}
		Suppose for contradiction $\sum_{j=0,1,2}\gamma_j = \frac{1}{g_{\EC}} - \epsilon$ for some $\epsilon >0$. Construct graph $G'$ by removing edge $f$ with $x_f\geq 1$ and replacing it with a path $P_f$ of length $\ceil{\frac{2}{\epsilon}}$. Define $x'_h = x_h$ for each edge $h$ such that $x_h<1$. For each $h\in P_f$ let $x'_h= x_f$ for all $f$ with $x_f\geq 1$. It is easy to check that $x'\in \EC(G')$. By Theorem \ref{CV} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and 2-edge-connected multigraphs $F'_i$ of $G'$ for $i=1,\ldots,k$ such that 
		$\sum_{i=1}^{k}\theta_i \chi^{F'_i}\leq g_{\EC}x'$.

		Note that each $F'_i$ contains at least one copy of every edge in any path $P_f$, except for at most one edge in the path. We will obtain 2-edge-connected multigraphs $F_1,\ldots,F_k$ of $G$ using $F'_1,\ldots,F'_k$, respectively. To obtain $F_i$ first remove all $P_f$ paths from $F'_i$. Suppose there is an edge $h$ in $P_f$ such that $\chi^{F'_i}_h=0$, this means that for any edge $p\in P_f$ such that $p\neq h$, $\chi^{F'_i}_p=2$. In this case, let $\chi^{F_i}_f=2$, i.e. add two copies of $f$ to $F_i$. If there are at least two edges $h,h'\in P_f$ with $\chi^{F'_i}_h=\chi^{F'_i}_{h'} = 1$, let $\chi^{F_i}_f=1$, i.e. add one copy of $f$ to $F_i$. If for all edge $h\in P_f$, we have $\chi^{F'_i}_h=2$, then let $\chi^{F_i}_f=2$. For $f\in E$ with $x_f<1$ we have
		\begin{equation}
		\sum_{i=1}^{k}\theta_i \chi^{F_i}_f=\sum_{i=1}^{k}\theta_i \chi^{F'_i}_f\leq g_{\EC}x'_f= g_{\EC}x_f.
		\end{equation}
		In addition for $f\in E$ with $x_f\geq 1$ we have $\chi^{F_i}_f \leq \frac{\sum_{h\in P_f}\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}$ by construction.
		\begin{align*}
			\sum_{i=1}^{k}\theta_i \chi^{F_i}_f&\leq \sum_{i=1}^{k}\theta_i\frac{\sum_{h\in P_f}\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}\\
			&= \frac{\sum_{h\in P_f} \sum_{i=1}^{k}\theta_i\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}\\
			&\leq \frac{\sum_{h\in P_f} g_{\EC}x'_h}{\ceil{\frac{2}{\epsilon}}-1}\\
			&= \frac{\sum_{h\in P_f} g_{\EC}x'_h}{\ceil{\frac{2}{\epsilon}}-1}\\
			&= \frac{\ceil{\frac{2}{\epsilon}}}{\ceil{\frac{2}{\epsilon}}-1}g_{\EC}x_f
		\end{align*}
		Therefore, we have 
		\begin{equation}
		x' \geq \sum_{i\in [k]: \chi^{F_i}_e=1}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}+\sum_{i\in [k]: \chi^{F_i}_e=2}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}.
		\end{equation}
		Let $x^j = \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}$ and $\theta_j =  \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}$ for $j=0,1,2$. It is easy to check that $x^j$ , $\theta_j$ for $j=0,1,2$ is a feasible solution to the LP above. Notice that $\sum_{j=0,1,2}\theta_j = \frac{\ceil{\frac{2}{\epsilon}}-1}{g_{\EC}\ceil{\frac{2}{\epsilon}}}$. By assumption, we have $\frac{\ceil{\frac{2}{\epsilon}}-1}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\leq  \frac{1}{g_{\EC}}-\epsilon$. However, this means $2\leq 1$ which is a contradiction.
	\end{proof}
	This concludes the proof. \end{proof}

@@

\begin{lemma}\label{2ecpruning}
	The FDT algorithm for 2EC in  polynomial time produces sets $L_0,\ldots,L_t$ of pairs $x\in \EC(G)$ together with multipliers $\lambda$ with the following properties.
		(a) If $x\in L_i$, then $x_{e_j}=0$ or $x_{e_j}\geq 1$ for $j=1,\ldots,i$, (b) $\sum_{(x,\lambda)\in L_i }\lambda \geq \frac{1}{g_{\EC}^i}$, (c) $\sum_{(x,\lambda)\in L_i }\lambda x \leq x^*$, (d) $|L_i|\leq t$.
\end{lemma}
The proof is similar to Lemma \ref{prune}, but we need to use property (v) in Lemma \ref{LPC2EC} to prove that (a) also holds.
\begin{proof}
	We proceed by induction on the $i$. Define $L_0=\{(x^*,1)\}$. It is easy to check all the properties are satisfied. Now, suppose by induction we have $L_{i-1}$ for some $i=1,\ldots,t$ that satisfies all the properties. For each solution $x^\ell$ in $L_{i-1}$ apply Lemma \ref{LPC2EC} on $x^\ell$ and $e_{i}$ to obtain $x^{\ell j}$ and $\lambda_{\ell j}$ for $j=0,1,2$. Let $L'$ be the collection that contains $(x^{\ell j},\lambda_\ell \cdot \lambda_{\ell j})$ for $j=0,1,2$, when applied to all $(x^\ell,\lambda_\ell)$ in $L_{i-1}$. Similar to the proof in Lemma \ref{prune} one can check that $L_i$ satisfies properties (b), (c). We now verify property (a). Consider a solution $x^\ell$ in $L_{i-1}$. For $e\in \{e_1,\ldots,e_{i-1}\}$ if $x^\ell_e =0$, then by property (iv) in Lemma \ref{LPC2EC} we have $x^{\ell j}=0$ for $j=0,1,2$. Otherwise by induction we have $x^{\ell}_{e}\geq 1$ in which case property (v) in Lemma \ref{LPC2EC} ensures that $x^{\ell j}_e\geq 1$ for $j=0,1,2$. Also, $x^{\ell j}_{e_i}= j$, so $x^{\ell j}_{e_i}=0$ or $x^{\ell j}_{e_i}\geq 1$ for $j=0,1,2$.

	Finally, if $|L'|\geq t$ we let $L_i=L'$, otherwise apply $\prun(L')$ to obtain $L_{i}$.
\end{proof}

### 2019-03-22 Journal Version/computational.tex
journal

\section{Computational experiments with FDT}\label{experiment}
\begin{figure}[h!]
\centering
\includegraphics[width=6.5cm]{"fdt vs christofides".png}
\caption{Christofides' algorithm vs FDT on all fundamental extreme points of order 10.}
\label{fdtvschris}
\end{figure}

We ran FDT on two covering problem: tree augmentation (TAP) and 2EC. For TAP we are given a tree $T=(V,E)$, and a set of non-edges $L$ between vertices in $V$ and costs $c\in \bbbr^{L}_{\geq 0}$. We wish to find the minimum-cost  $L'\subseteq L$ such that $T+L'$ is 2-edge-connected. For $\ell\in L$, let $P_\ell$ be the set of edges in the unique path between the endpoints of $\ell$ in $T$. For TAP, $S(\mbox{TAP})=\{x\in \bbbz^{L}_{\geq 0}: \sum_{\ell: e\in P_\ell}x_\ell \geq 1, \mbox{ for $e\in E$}\}$ and $P(\mbox{TAP})$ relaxes integrality. We know $\frac{3}{2}\leq g({\mbox{TAP}})\leq 2$~\cite{fj,32gap}. We ran binary FDT on a set of 264 fractional extreme points of $P(\mbox{TAP})$. Table \ref{tableTAP} shows FDT found solutions better than the integrality-gap lower bound for most instances.

We also implemented the polyhedral version of Christofides' algorithm \cite{Wolsey1980}. Figure \ref{fdtvschris} shows FDT's solutions on fundamental extreme points of order 10 are always better than those from Christofides' algorithm.
\vspace*{-.2in}
\begin{table}[h!]
\begin{small}
	\centering
	  \begin{tabular}{c c c c c}
	  \toprule
	  	& $C\in [1.1,1.2]\;$ & $\;C\in (1.2,1.3]\;$ &
               $\;C\in (1.3,1.4]$ &\; $C\in (1.4,1.5]\;$ \\ \midrule
	  	TAP & $36$ & $66$ & $170$ & $10$\\  \bottomrule \\
	  \end{tabular}\caption{The scale factor $C$ for FDT run on 264 randomly generated TAP instances with fractional extreme points: 138 instances have $74$ variables. The rest have $250$.}
\end{small}
	  \label{tableTAP}
\end{table}
%\vspace*{-30pt}
We ran FDT for 2EC on 963 fractional extreme points of $\EC(G)$. We enumerated all fundamental vertices of order $10$ and $12$. Table \ref{table2EC} shows that again FDT found solutions better than the integrality-gap lower bound for most instances. 
\begin{table}[h!]
\begin{small}
	\centering
	  \begin{tabular}{c c c c c}
	  	\toprule
	  	& $C\in [1.08,1.11]\;$ & $\;C\in (1.11,1.14]\;$ &
               $\;C\in (1.14,1.17]$ &\; $C\in (1.17,1.2]\;$ \\ \midrule
	  	2EC & $79$ & $201$ & $605$ & $78$ \\ \bottomrule\\
	  \end{tabular}	\caption{FDT for $\EC$ implemented applied to all fundamental extreme points of order 10 or 12. A FEP of order $k$ has $\frac{3k}{2}$ variables. The lower bound on $g(\EC)$ is $\frac{6}{5}$.}
	  \label{table2EC}
\end{small}
\end{table}

>>>>

\section{Computational experiments with FDT}\label{experiment}
We ran FDT on two covering problems: the tree augmentation problem (TAP) and 2EC. In TAP we are given a tree $T=(V,E)$, and a set of non-edges $L$ between vertices in $V$ and costs $c\in \mathbb{R}^{L}_{\geq 0}$. A feasible augmentation is $L'\subseteq L$ such that $T+L'$ is 2-edge-connected. In TAP we wish to find the minimum-cost feasible augmentation.

For $\ell\in L$, let $P_\ell$ be the set of edges in the unique path between the endpoints of $\ell$ in $T$. Let $\TAP(T,L)=\{x\in [0,1]^{L}: \sum_{\ell: e\in P_\ell}x_\ell \geq 1, \mbox{ for $e\in E$}\}$. Then $\TAP(T,L)\cap \mathbb{Z}^{L}$ is set of feasible augmentations for the instance defined by $T$ and $L$. We know $\frac{3}{2}\leq g_{\TAP}\leq 2$~\cite{fj,32gap}. We ran binary FDT on a set of 264 fractional extreme points of randomly produces instances of $\TAP$. Table \ref{tableTAP} shows FDT found solutions better than the integrality-gap lower bound for most instances.

\begin{table}[h!]
	\begin{small}
		\centering
		\begin{tabular}{c c c c c}
			\hline
			& $C\in [1.1,1.2]\;$ & $\;C\in (1.2,1.3]\;$ &
			$\;C\in (1.3,1.4]$ &\; $C\in (1.4,1.5]\;$ \\ \hline
			TAP & $36$ & $66$ & $170$ & $10$\\  \hline \\
		\end{tabular}\caption{The scale factor $C$ for FDT run on 264 randomly generated TAP instances with fractional extreme points: 138 instances have $74$ variables. The rest have $250$.} \label{tableTAP}
	\end{small}

\end{table}

We also implemented the polyhedral version of Christofides' algorithm \cite{Wolsey1980}. In particular, we implemented the $T$-join augmentation in Christofides' algorithm, in a way that minimizes the average usage of every edge across the the convex combination of spanning trees. This allows the ``real'' approximation ratio of Christofides' algorithm to be below $\frac{3}{2}$. Figure \ref{fdtvschris} shows FDT's solutions on all FEPs of order 10 are always better than those from Christofides' algorithm.

\begin{figure}[h!]
	\centering
	\includegraphics[width=6.5cm]{"fdt vs christofides".png}
	\caption{Christofides' algorithm vs FDT on all fundamental extreme points of order 10.}
	\label{fdtvschris}
\end{figure}

We ran FDT for 2EC on 963 fractional extreme points of $\EC(G)$. We enumerated all fundamental vertices of order $10$ and $12$. Table \ref{table2EC} shows that again FDT found solutions better than the integrality-gap lower bound for most instances. 
\begin{table}[h!]
\begin{small}
	\centering
	  \begin{tabular}{c c c c c}
	  	\hline
	  	& $C\in [1.08,1.11]\;$ & $\;C\in (1.11,1.14]\;$ &
               $\;C\in (1.14,1.17]$ &\; $C\in (1.17,1.2]\;$ \\ \hline
	  	2EC & $79$ & $201$ & $605$ & $78$ \\ \hline\\
	  \end{tabular}	\caption{FDT for $\EC$ implemented applied to all fundamental extreme points of order 10 or 12. A FEP of order $k$ has $\frac{3k}{2}$ variables. The lower bound on $g_{\EC}$ is $\frac{6}{5}$.}
	  \label{table2EC}
\end{small}
\end{table}
